---
editor: visual
engine: knitr
filters:
  - webr
---

## #TidyTuesday + WebR

[WebR](https://docs.r-wasm.org/webr/latest/) is a version of R that runs in the browser.
You don't need to install R and no one needs to setup a server.
It just runs on your local computer (or even your phone), but through your browser.
This site lets you use it for this weeks Tidy Tuesday using the long-term monitoring data on mammals from [the Portal Project](https://portal.weecology.org). 

## Data

The dataset is a on the long-term dynamics of rodent species. It has three tables:

* `surveys` - which has one row for each individual animal caught including where, when, and information on the individual like size
* `species`, which has one row for each species in the dataset
* `plots`, which has one row per plot that tells you if the plot is a `control` plot or an `exclosure` plot where the dominant kangaroo rat species have been excluded.

::: {.callout-tip collapse="true"}

## Show. Me. The. Data.
```{r}
#| echo: false
#| output: false
surveys <- read.csv("https://tidytuesday.weecology.org/surveys.csv", na.strings = c(""))
species <- read.csv("https://tidytuesday.weecology.org/species.csv", na.strings = c(""))
plots <- read.csv("https://tidytuesday.weecology.org/plots.csv")
```

```{r}
head(surveys)
```

```{r}
head(species)
```

```{r}
head(plots)
```

:::

## Let's go!

There are three WebR-enabled pages on this site:

1. [Getting Started](/getting-started.qmd) - will walk you through loading the data and installing packages in WebR
2. [Base R](/base.qmd) - gives you a Base R only setup with the data already loaded
3. [Tidyverse](/tidyverse.qmd) - gives you R + dplyr + ggplot2 and the data already loaded. _This page takes about 20 seconds to load the packages_

## What is this magic?!?

If you want to see how all of this works you can checkout the [GitHub repository](https://github.com/weecology/tidy-tuesday-portal) for this site.
The site uses [Quarto](https://quarto.org/) with the [Quarto WebR extension](https://github.com/coatless/quarto-webr).
Preloading data on the [Base](/base.qmd) and [Tidyverse](/tidyverse.qmd) pages requires a [little bit of javascript](https://github.com/weecology/tidy-tuesday-portal/blob/1e0887f63fb1918ff5df6271a77bfceba01c5db6/base.qmd#L9-L23).