---
title: Portal Project Tidy Tuesday - Tidyverse
editor: visual
engine: knitr
filters:
  - webr
webr:
  packages: ['ggplot2', 'dplyr']
---

<html>
<script type="module">
//=== Load data on load ===
import { WebR } from 'https://webr.r-wasm.org/latest/webr.mjs'; 
globalThis.webR = new WebR(); 
await globalThis.webR.init(); 
globalThis.webRCodeShelter = await new globalThis.webR.Shelter();
let surveys = await globalThis.webR.evalR('read.csv("https://tidytuesday.weecology.org/surveys.csv", na.strings = c(""))')
await webR.objs.globalEnv.bind('surveys', surveys)
let species = await globalThis.webR.evalR('read.csv("https://tidytuesday.weecology.org/species.csv", na.strings = c(""))')
await webR.objs.globalEnv.bind('species', species)
let plots = await globalThis.webR.evalR('read.csv("https://tidytuesday.weecology.org/plots.csv")')
await webR.objs.globalEnv.bind('plots', plots)
</script>
</html>

```{r}
#| echo: false
#| output: false
surveys <- read.csv("https://tidytuesday.weecology.org/surveys.csv", na.strings = "")
species <- read.csv("https://tidytuesday.weecology.org/species.csv", na.strings = "")
plots <- read.csv("https://tidytuesday.weecology.org/plots.csv")
```

::: {.callout-note collapse="true"}

## The data
There are three tables in this dataset.

`surveys`, which has one row for each individual animal caught:

```{r}
head(surveys, n = 3)
```

`species`, which has one row for each species in the dataset:

```{r}
head(species, n = 3)
```

`plots`, which has one row per plot that tells you if the plot is a `control` plot or an `exclosure` plot where the dominant kangaroo rat species have been excluded.

```{r}
head(plots, n = 3)
```

:::

```{webr-r}
```